Statement of Purpose

### 2020-08-26 Records/scholarships/personal-statement.tex
Cleaned up old stuff and created 451 folder
Signed-off-by: Haataja <grant.haataja@undcemlh112-29l.cem.und.edu>

I have paid my own way in life since I started attending Williston State College at age 16. My parents make enough money to prevent me from receiving financial aid, but not enough for them to help me pay for my school. I have worked summer internships for up to 100 hours a week, I have had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.

>>>>

I have paid my own way in life since I started attending Williston State College at age 16. My parents make enough money to prevent me from receiving financial aid, but not enough for them to help me pay for my school. I have worked summer internships for up to 100 hours a week, had jobs while taking up to 20 credits in a semester, and found every opportunity I could to make my dreams a reality.

### 2020-08-26 Records/scholarships/resume2.tex
Cleaned up old stuff and created 451 folder
Signed-off-by: Haataja <grant.haataja@undcemlh112-29l.cem.und.edu>

\subsection{University of North Dakota:}
Double major in Computer Science and Mathematics with a current cumulative GPA of 3.80. Expected Graduation Date: 12/2020

@@

\subsection{Association of Computing Machinery:}
Participate in regional programming competitions

@@

\subsubsection{Helix Wine \& Bites (01/18/19 - Current)} 
\textbf{Bartender/Server:} Providing exceptional food and drink service to customers

>>>>

\subsection{University of North Dakota:}
Double major in Computer Science and Mathematics with a current cumulative GPA of 3.75. Expected Graduation Date: 12/2020

@@

\subsection{Association of Computing Machinery:}
Acting president of club, organizing meetings and training and participating in regional programming competitions

@@

### 2020-08-26 Records/scholarships/statement_of_purpose.tex
Cleaned up old stuff and created 451 folder
Signed-off-by: Haataja <grant.haataja@undcemlh112-29l.cem.und.edu>

\documentclass[11pt,final,twoside]{article} %setup
%set margins and load symbols and such
\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
marginparwidth=23mm,marginparsep=4mm]{geometry}
%header of document
\title{Personal Statement}
\author{Grant Haataja}
\date{\today}
%set paragraph spacing
\linespread{1.5}

@@

That is why I have chosen to study Mathematics and Computer Science, whose very foundations are built on problem solving. My greatest interest is to study and research coding theory, which lies directly at the intersection of Math and Computer Science. With a strong background in both subjects, I feel that I can bring a broader perspective to my research.

@@

I am currently working 2 jobs for a total of around 40 hours per week, while taking 16 credits and acting as co-lead of the software development team for Advanced Rocketry Club on campus. The US MASTER scholarship would help immensely to take some of my workload stress off my shoulders and allow me to focus more deeply on my classes and exciting research opportunities.

My career goals are to graduate with a double major and research experience, work in my field to learn real-world applications and provide service to society, and eventually return to graduate school and become a professor at a university so I can continue to pursue my passion for Math and research, as well as help other students reach their full potential.

>>>>

\documentclass[11pt,final,twoside]{article} %setup
%set margins and load symbols and such
\usepackage[top=20mm,inner=20mm,outer=30mm,bottom=20mm,
marginparwidth=23mm,marginparsep=4mm]{geometry}
%header of document
\title{Statement of Purpose}
\author{Grant Haataja}
\date{\today}
%set paragraph spacing
\linespread{1.5}

@@

That is why I have chosen to study Mathematics and Computer Science, whose very foundations are built on problem solving. My greatest interest is to study and research cutting-edge technologies for ciphers and cybersecurity, which lie directly at the intersection of Math and Computer Science. With a strong background in both subjects, I feel that I can bring a broader perspective to my research.

@@

I am currently working 2 jobs for a total of around 40 hours per week, while taking 16 credits and acting as co-lead of the software development team for Advanced Rocketry Club on campus. The NYIT REU program would be an exciting research opportunity for the summer where I could cut down on my responsibilities in order to focus exclusively on research and learning of topics I am fascinated with.

My career goals are to graduate with a double major and research experience, work in my field to learn real-world applications and provide service to society, and eventually return to graduate school and become a professor at a university so I can continue to pursue my passion for cybersecurity and research, as well as help other students reach their full potential.
